---
title: "Rendering SSURGO Polygons using SDA WMS and leaflet package"
output: html_notebook
---

 

```{r}
library(leaflet)

wms_nrcs <- 'https://SDMDataAccess.sc.egov.usda.gov/Spatial/SDM.wms'

leaflet() %>% 
    addTiles() %>%
  setView(lng = -121.287638, lat = 40.703039, zoom = 15) %>% 
    addWMSTiles(
        wms_nrcs,
        layers = c("SurveyAreaPolyOutline","MapunitPolyExtended",'featpoint'),
        options =  c(WMSTileOptions(format = "image/png", transparent = TRUE),labelOptions(interactive=TRUE))
    ) %>%
  addWMS(
        wms_nrcs,
        layers = "MapunitPoly",
        popupOptions = popupOptions(maxWidth = 600),
        options = WMSTileOptions(
          transparent = TRUE,
          format = "image/png",
          info_format = "text/html")
    )


```


```{r}
library(sf) # simple features packages for handling vector GIS data
library(httr) # generic webservice package
library(tidyverse) # a suite of packages for data wrangling, transformation, plotting, ...
library(ows4R) # interface for OGC webservices
```

# Tutorial on interfacing with WFS in R
https://inbo.github.io/tutorials/tutorials/spatial_wfs_services/

We append information to the URL address with the aid of *httr::parse_url* and *httr::build_url*. The former function parses an URL into a list for easier programmatic addition of information to the URL. The latter function does the reverse and builds the URL from the list object.

The *url$query* slot is where you instruct the WFS what information it should return. It is constructed as a list with name-value pairs. For now, we only need to specify the GetCapabilities request. Other information such as passing version = 2.0.0 can be added, but is not required (by default, the latest version of the WFS service will be chosen).
```{r}
wfs_bwk <- "https://sdmdataaccess.nrcs.usda.gov/Spatial/SDM.wms"

url <- parse_url(wfs_bwk)
url$query <- list(service = "wfs",
                  #version = "2.0.0", # facultative
                  request = "GetCapabilities"
                  )
request <- build_url(url)
request
```

Get to know what the service can do with GetCapabilities
```{r}
bwk_client <- WFSClient$new(wfs_bwk, 
                            serviceVersion = "1.1.1") #service Version must be provided here

bwk_client$getFeatureTypes(pretty = TRUE)

bwk_client$getCapabilities()

bwk_client$
  getCapabilities()$
  findFeatureTypeByName("mapunitlineextended")$
  getDescription() %>%
  map_chr(function(x){x$getName()})
#OR
bwk_client$
  describeFeatureType(typeName = "mapunitpolyextended") %>%
  map_chr(function(x){x$getName()})


#Here is how to get a character vector naming all available operations of the WFS:
bwk_client$
  getCapabilities()$
  getOperationsMetadata()$
  getOperations() %>%
  map_chr(function(x){x$getName()})



#output formats
bwk_client$
  getCapabilities()$
  getOperationsMetadata()$
  getOperations() %>%
  map(function(x){x$getParameters()}) %>%
  pluck(3, "outputFormat")

#extract the bounding boxes for all layers
bwk_client$
  getCapabilities()$ 
  getFeatureTypes() %>%  
  map(function(x){x$getBoundingBox()})

#get the abstract for layers
bwk_client$
  getCapabilities()$ 
  getFeatureTypes() %>%  
  map_chr(function(x){x$getAbstract()})
```

Read or download vector data from WFS: GetFeature
```{r}
bwk_client$getFeatureTypes(pretty = TRUE)

url <- parse_url(wfs_bwk)
url$query <- list(service = "wfs",
                  #version = "2.0.0", # facultative
                  request = "GetFeature",
                  typename = "mapunitpolyextended",
                  bbox = "-121.77100,37.368402,-121.76000,37.373473")

request <- build_url(url)
request

st_layers(request)

poly_extend <- read_sf(request)

ggplot(poly_extend) + 
  geom_sf()

```

```{r}
query <- list(service = "WFS",
             request = "GetFeature",
             #version = "1.1.0", # optional
             typeName = "mapunitpolyextended",
             outputFormat = "text/xml; subtype=gml/3.1.1",
             propertyname = as.character(paste(properties_of_interest,
                                               collapse = ",")),
             CRS = "EPSG:31370",
             CQL_FILTER = sprintf("INTERSECTS(geom,POINT(%s %s))",
                                  x_lam, y_lam)) 
result <- GET(wfs_bwk, query = query)
result
```

